A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-08-26 refl_maths/paper.tex
overfitting section updated

>>>>

\section{Overfitting}

Main points
1. Rule of thumb - simple the better but what does it mean
2. Way to quantify information content without model doesn't exist but gain of information with the model can be estimated
3. Bayesian model selection provides statistically sound way of testing hypotesis
4. Combining different sources of information increase information content but requires proper methodology

When defining a model care must be taken to balance the complexity of the model with the fit to the data.
By using too few parameters we risk that important structural features are not covered by the model and that fit to data is worse than optimal. 
However overparamaterizng the model may lead to overfitting to the data and therefore deriving false conclusions about the measured sample. 
The latter issue is particularly problematic for reflectometry data for which information content/density is typically low. 
Different strategies have been used to address overfitting in reflectometry. Typically a "rule of thumb" of choosing the most simple model that enables a description
of the data [Mccluskey, 2020] has been applied. Even though such method is easy to apply it requires prior knowledge about the sample (e.g. from different experiment) and making assumption about information content in the data i.e. do we have enough information to support the model. 
The information content can in principle be quantified directly from the data as has been widely demonstrated for small-angle scattering data, which also typically suffers from limited structural information [Moore, 1980, Taupin & Luzzati, 1982; Luzzati & Taupin, 1986 ; Müller et al., 1996 ; Vestergaard & Hansen, 2006 ; Pedersen et al., 2014; Konarev & Svergun, 2015; Larsen et al., 2018] or by validating model given the data. 
The example of latter approach uses Bayesian model selection framework to compare models with different numbers of parameters to determine which  offers the maximum information without over-fitting. [Hughes Biophys. J.116, 1095 (2019); Mccluskey https://arxiv.org/pdf/1910.10581.pdf]. While this approach provides rigours framework for finding "optimal" model it is also important to note that it depends on the prior probabilities chosen for each of the parameters.
The problem of finding an optimal model can also be inverted to another task of acquiring "optimal" data that can support given model. Treece et al. developed a method based on Bayesian statistics and information theory that quantifies information gain from reflectometry experiments with the purpose of guiding experimental design \cite{Treece_2019}. 
Regardless of the method used to mitigate over-fitting, we are limited to information covered by the data. To overcome this limitation one can combine information from other techniques. This can be done by constraining model parameters with literature values or by simultaneously fitting model against experimental data from other techniques e.g. X-ray and neutron refelectometry. This is however challenging because different part of the curve may contain different information and proper reweighing needs to be done, which again can be mitigated by the use of Bayesian statistics.
